Species motif participation provides unique information about species risk of extinction

### 2023-04-14 manuscript/reorder_main_text.tex

        Species' motif participation also varied with their in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}).
        Species with higher in-degree tended to have higher frequencies of participation in the omnivory motif. Proportions of the other three motifs tended to decline with increasing degree.
        Species with higher trophic levels tended to have higher proportions of apparent competition and three-species chains. 
        A species' persistence varies with both species in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}; \emph{Appendix S6}). 
        Increased trophic level is generally associated with decreasing species persistence, although the rate of decline is slower at high disturbance (Table S3, \emph{Appendix S6}).
        In-degree shows an even stronger interaction with disturbance; having more prey species is associated with higher persistence without disturbance, but lower persistence at high levels of disturbance.

@@

        \begin{figure}[hb!]
        \centering
        \includegraphics[width=0.85\textwidth]{figures/persistence_vs_motifs.eps}
        \caption{The effect of proportion of the role (x-axis) made up by various motifs (columns) on persistence (y-axis). The effect of participating in each motif is based on the fixed effects in Equation~\ref{propreq}. The different colored lines indicate the probability of extinction of basal species, from $\pi_{disturbed} = 0.1$ (top, purple; no disturbance) to $\pi_{disturbed} = 0.5$ (bottom, yellow; high disturbance). 95\% confidence intervals for each line are shown in grey. Note that omnivory made up a smaller proportion of species' roles than other motifs; lines are plotted over the observed ranges of motif participation.}
    \label{fig:prop_lmer_all}
    \end{figure}

>>>>

        Species' motif participation also varied with their in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}).
        Species with higher in-degree tended to have higher frequencies of participation in the omnivory motif and lower proportions of the other three motifs.
        Species with higher trophic levels tended to have higher proportions of apparent competition and three-species chains and lower proportions of omnivory and direct competition. 
        A species' persistence varies with both species in-degree and trophic level (Fig.~\ref{fig:motifs_vs_TL_and_deg}; \emph{Appendix S6}). 
        Increased trophic level is generally associated with decreasing species persistence, although the rate of decline is slower at high disturbance (Table S3, \emph{Appendix S6}).
        In-degree shows an even stronger interaction with disturbance; having more prey species is associated with higher persistence without disturbance, but lower persistence at high levels of disturbance.

@@

        \begin{figure}[hb!]
        \centering
        \includegraphics[width=0.85\textwidth]{figures/persistence_motif_participation.eps}
        \caption{The effect of proportion of the role (x-axis) made up by various motifs (columns) on persistence (y-axis). The effect of participating in each motif is based on the fixed effects in Equation~\ref{propreq}. The different colored lines indicate the probability of extinction of basal species, from $\pi_{disturbed} = 0.1$ (top, purple; no disturbance) to $\pi_{disturbed} = 0.5$ (bottom, yellow; high disturbance). 95\% confidence intervals for each line are shown in grey. Note that omnivory made up a smaller proportion of species' roles than other motifs; lines are plotted over the observed ranges of motif participation.}
    \label{fig:prop_lmer_all}
    \end{figure}
